---
title: "Himalyan Climber"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(dplyr)
library(tidyr)
library(ggplot2)
library(highcharter)
library(echarts4r)
library(data.table)
library(vroom)
library(janitor)
```

```{r load data}
expeditions <- fread("Himalayan Climber/data/expeditions.csv")%>%clean_names()
members <- fread("Himalayan Climber/data/members.csv")%>%clean_names()
peaks <- fread("Himalayan Climber/data/peaks.csv")%>%clean_names()
```


```{r glimpse expeditions}
glimpse(expeditions)
```

```{r glimpse members}
glimpse(members)
```

```{r glimpse peaks}
glimpse(peaks)
```

# Start with peaks

* How many peaks are already climbed and how many still remained unclimbed
* distribution of heights

```{r}
ggplot(peaks) + geom_histogram(aes(height_metres),binwidth=100,fill="royalblue") + theme_minimal()
```
## Questions in this analysis

* Climbing status of mountain
* Peaks distribution 
* Which country has highest number of climbers
* In which year most death occured and success occured?
* Hired people are injured or Climbers are injured?
* Age group of climbers and Hired people
* which mountain is risky and in which season?



```{r missing values in peaks}
peaks%>%is.na()%>%colSums()
```

```{r climbing status}
peaks%>%group_by(climbing_status)%>%
    summarise(count=n())%>%
    mutate(percent = round(count/sum(count)*100,2))
```
* Out of 468 peaks in himalayan region , 341 is climbed i.e 72.86 % and 127 is still unclimbed i.e 27.14.


```{r}
climb_status<-peaks%>%group_by(climbing_status)%>%
    summarise(count=n())%>%
    mutate(percent = round(count/sum(count)*100,2))

    ggplot(climb_status)+
    geom_col(aes(x=climbing_status,count,fill=climbing_status))+
        labs(title="Climbing Status of Himalyan Peaks",x="count",y="Climbing Status")+
        theme_minimal()+
        theme(legend.position = "")
```

### First Ascent year

```{r}
peaks%>%
    filter(climbing_status=="Climbed")%>%
    group_by(first_ascent_year)%>%
    summarise(n())
```

Here one peak has ascent year of 201 ,lets check which peak is this?

```{r}
peaks%>%filter(first_ascent_year==201)
```

The peak is Sharphu II which was climbed in 2018 . So i will replace 201 with 2018 for sharphhu 2.

```{r}
peaks[first_ascent_year==201]$first_ascent_year <- 2018
```


```{r}
peaks%>%
    filter(climbing_status=="Climbed")%>%
    group_by(first_ascent_year)%>%
    summarise(n())
```

After sorting the 'Sharphu 2' now we have 6 NA values for peaks with climbed status.
Lets check which mountain are these.

```{r}
peaks%>%filter(climbing_status=="Climbed" & is.na(first_ascent_year))
```

I m looking into the google to find the first date of ascent for these mountains.

Naya Kanga - 1953
Khongma Tse - 1991 
Nirekha - 2003
Jinjang - 1960 
Herzog Peak - 1950
Nuptse West II - 1961

```{r}
peaks[peak_name=="Naya Kanga"]$first_ascent_year <- 1953
peaks[peak_name=="Khongma Tse"]$first_ascent_year <- 1991
peaks[peak_name=="Nirekha"]$first_ascent_year <- 2003
peaks[peak_name=="Jinjang"]$first_ascent_year <- 1960
peaks[peak_name=="Herzog Peak"]$first_ascent_year <- 1950
peaks[peak_name=="Nuptse West II"]$first_ascent_year <- 1961
```


```{r}
first_ascent_df <- peaks%>%
    filter(climbing_status=="Climbed")%>%
    group_by(first_ascent_year)%>%summarise(count=n())
```

```{r}
ggplot(first_ascent_df)+
    geom_col(aes(first_ascent_year,count))+
    theme_minimal()
```

```{r}
ggplot(peaks%>%filter(climbing_status=="Climbed"))+
    geom_histogram(aes(first_ascent_year),binwidth = 5)+
    theme_minimal()
```


# Which country has highest number of climbers

```{r}
members%>%
    group_by(citizenship)%>%
    summarise(count=n())%>%arrange(-count)
```

# Most death occured by year

```{r}
members%>%
    filter(success==TRUE)%>%
    group_by(year)%>%
    summarise(count = n())%>%
    arrange(-count)
```

* In 2018 1862 climbers climbed himalayan peaks successfully
* In 1985,89 34 climbers died 

```{r}
members%>%
    filter(died==TRUE)%>%
    group_by(year)%>%
    summarise(count = n())%>%
    arrange(-count)

```

## EDA on members df

```{r}
glimpse(members)
```

```{r}
members%>%is.na()%>%colSums()
```

```{r}
members%>%
    group_by(hired,injured)%>%
    summarise(count=n())
```

## Age group of climbers and Hired people

```{r}
climber_age_df <- members%>%
    group_by(hired,age)%>%
    summarise(count=n())
```

```{r}
climber_age_df%>%mutate(age_group = 
                            case_when(age >=0 & age <=10 ~ "0 to 10",
                                      age >=11 & age <=20 ~ "5 to 10",
                                      age >=21 & age <30 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10",
                                      age >=5 & age <11 ~ "5 to 10"
                                      ))
```

